---
title: "HW2"
author: "Ziran Xu"
date: "3/6/2019"
output:
  html_document:
    df_print: paged
  pdf_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Q1
Since f(x) = 2 *exp(-2*x) then F(x) is the integration of f(x).
   F(x) = 1-exp(-2*x)
   U = 1-exp(-2*x)
   so x = -log(1-U) / 2   
Hence need to generate 100 uniform random numbers from 0 to 1
Then can generate random sample size 100 from this distribution
```{r}
u1 = runif(100,min = 0,max = 1)
randnum_Q1 = -log(1-u1) / 2
mean_Q1 = mean(randnum_Q1)
var_Q1 = var(randnum_Q1)    
cat("The mean and Var are ",mean_Q1,var_Q1,"\n\n")
fit = lm(randnum_Q1~log(1-u1))
summary(fit)
```
Hence the EDF is x = -5.000e-01*log(1-u)

## Q2
Since the variance is 1 and the variance of the double exponential distribution is 2*beta^2. Hence the beta = 1/sqrt(2). From the question abs(beta) = k , k = 1/sqrt(2). C = 1/(2*beta) then C = sqrt(2) / 2.
   g(x) = sqrt(2) * exp(-abs(x)/sqrt(2)) / 2
   f(x) = exp(-x^2/2) / sqrt(2*pi)
   M >= f(x)/g(x) hence M = max(f(x)/g(x)) = 0.7244 while x = +/- 1/sqrt(2)
   
```{r}
x2 = rnorm(100)
u2 = runif(100)
y2 =rep(NA,100)
M = 0.7244
for(i in 1:100)
{
  if((exp(-(x2[i])^2/2) / sqrt(2*pi)) /(M*sqrt(2) * exp(-abs(x2[i])/sqrt(2)) / 2) >u2[i])
    y2[i] = x2[i]
}
y2 =na.omit(y2)
cat("The resulting sample size is",length(y2))
```
## Q3
while alpha = 3, the first integration is 3*x*exp(-3*x) from [0,Inf) and the second integration is 3*log(x)*exp(-3*x) from [0,Inf).

```{r}
u3 = runif(100,min = 0,max = 1)
num3_1 = -log(1-u3)/3  # generate the exponential r.v
inte_3_11 = mean(num3_1)  # the first integral is the expectation of exponential distribution
inte_3_12 = mean(log(num3_1))   # the second integral is the expectation of log fucntion with exponential distribution
cat("The first integral is ",inte_3_11,"and the second integral is",inte_3_12)
```
while alpha = 4, the first integration is 4*x*exp(-4*x) from [0,Inf) and the second integration is 4*log(x)*exp(-4*x) from [0,Inf)
```{r}
num3_2 = -log(1-u3)/4  # generate the exponential r.v
inte_3_21 = mean(num3_2)  # the first integral is the expectation of exponential distribution
inte_3_22 = mean(log(num3_2))   # the second integral is the expectation of log fucntion with exponential distribution
cat("The first integral is ",inte_3_21,"and the second integral is ",inte_3_22)
```
## Q4
First generate the r.v from uniform distribution then change into the possion distrition. Finally calculate the P(x>2)
```{r}
u4 = runif(100,min = 0,max = 1)
num4 = 1:length(u4)
f4 = function(x,u)
{
  return(1.5^x*exp(-1.5)/prod(1:x)-u)
}
for(i in 1:length(u4))
{
  root = uniroot(f4,c(0,1000),u = u4[i])
  num4[i] = root$root
}
p = length(num4[num4>2])/length(num4)
cat("The P(X>2) = ",p)
```
## Q5
Since here alpha = 4 and lambda is 2. xi ~ Exp(2) then Y = sum(xi) from 1 to 4.

```{r}
num5_gamma = 1:100
p5 = rep(1,100)
for(i in 1:100)
{
  u5 = runif(4,min = 0,max = 1)
  num5 = -log(1-u5) /2
  num5_gamma[i] = sum(num5)  #gamma distribution Gamma(4, 2) as a sum of exponentials.
  for(j in 1:4)
  {
    p5[i] = p5[i]*(1-exp(-2*num5[j]))  # since they are independent so can multiply
  }
}
cat("The gamma random numbers are ",num5_gamma,"\nThen probability corresponded with these numbers are ",p5)
```
Then can get more random numbers to fit CDF function, then also can get the PDF.

For the Accept-reject technique. The g(x) = gamma(2,1) and f(x) = gamma(4,2)
Then find the M >= f(x)/g(x) = 1.444 when x = 2
```{r}
y5 = rep(NA,100)
x5= 1:100
M = 1.44
for(i in 1:100)
{
  u5 = runif(4,min = 0,max = 1)
  num5 = -log(1-u5) /2
  x5[i] = sum(num5)  #gamma distribution Gamma(4, 2) as a sum of exponentials.
}
u5_2 = runif(100,min = 0,max = 1)
for(i in 1:100)
{
  if((8*x5[i]^2*exp(-x5[i])/(3*M))>u5_2[i])
{
  y5[i] = x5[i]
}
}
y5 = na.omit(y5)
cat("The random number from gamma(2,1) are ",y5)
```
## Q6
Since as the question required we need 100 simulations and n =100
To calcualte the E(x^2) then calculate the sum(xi^2)/(2*n) from 1 to 2*n
```{r}
u6 = runif(100,min = 0,max = 1)
un6 = 1-u6   # antithetic values
s= 0
for(i in 1:100)
{
  s = s+u6[i]^2+un6[i]^2
}
result1 = s/200  
cat("The E(x^2) is",result1)
```
To cauculate the Var(h2n) , h(x) = x^2. Need to get the E(x) first, then Var(h2n) = E(x^2) - (E(x))^2
```{r}
s = 0
for( i in 1:100)
{
  s = s +u6[i]+un6[i]
}
result2 = s/200
cat("The Var(h2n) is ",result1-result2^2)
```
## Q7
From the question request 100 simulations with n = 100.
h(x) = x^2 and g(x) =x.
To calculate the E(x^2) and Var(hCV)
E(x^2) = E(h(x)-g(x)) +E(g(x)) = sum(h(xi) - g(xi))/n + sum(g(xi))/n 
Var(hCV) = Var(sum(h(xi)-g(xi))/n^2) = sum(Var(h(Xi))+Var(g(Xi))-2*cov(h(Xi),g(Xi)))/n^2
```{r}
u7 = runif(100,max = 1,min = 0)
s1=0
s2=0
mean1 = mean(u7^2)
mean2 = mean(u7)
for(i in 1:100)
{
  s1 = s1+(u7[i]^2-u7[i])
  s2 = s2+u7[i]
}
result1 = s1/100+s2/100
cat("The E(x^2) is ",result1)
s3=0
for(i in 1:100)
{
  s3 = s3+(u7[i]^2-mean1)^2+(u7[i]-mean2)^2-2*(u7[i]^2-mean1)*(u7[i]-mean2)
}
result2 = (s3)/100^2
cat("\nThe Var(hCV) is ",result2 )
```
## Q8
From the question request 100 simulations with n = 100.
```{r}
u81 = runif(20,min = 0,max = 0.2)
u82 = runif(20,min = 0.2,max = 0.4)
u83 = runif(20,min = 0.4,max = 0.6)
u84 = runif(20,min = 0.6,max = 0.8)
u85 = runif(20,min = 0.8,max = 1)
mean11 = mean(u81^2)
mean12 = mean(u82^2)
mean13 = mean(u83^2)
mean14 = mean(u84^2)
mean15 = mean(u85^2)
mean21 = mean(u81)
mean22 = mean(u82)
mean23 = mean(u83)
mean24 = mean(u84)
mean25 = mean(u85)
s1 = 0
for(i in 1:20)
{
  s1 = s1 +u81[i]^2+u82[i]^2+u83[i]^2+u84[i]^2+u85[i]^2
}
result1 = s1/100
cat("The E(x^2) is ",result1)
s2=0
for(i in 1:20)
{
  s3 = s3+(u81[i]^2-mean11)^2+(u81[i]-mean21)^2-2*(u81[i]^2-mean11)*(u81[i]-mean21)+(u82[i]^2-mean12)^2+(u82[i]-mean22)^2-2*(u82[i]^2-mean12)*(u82[i]-mean22)+(u83[i]^2-mean13)^2+(u83[i]-mean23)^2-2*(u83[i]^2-mean13)*(u83[i]-mean23)+(u84[i]^2-mean14)^2+(u84[i]-mean24)^2-2*(u84[i]^2-mean14)*(u84[i]-mean24)+(u85[i]^2-mean15)^2+(u85[i]-mean25)^2-2*(u85[i]^2-mean15)*(u85[i]-mean25)
}
result2 = s3/100^2
cat("\nThe Var(hCV) is ",result2 )
```
## Graphs in Q1 
```{r pressure, echo=FALSE}
hist(randnum_Q1,breaks = 8,main = "Histogram of Q1",xlab = "random numbers of Q1")
```
```{r pressure, echo=FALSE}
plot(x= u1 ,y = randnum_Q1,,ylim =c(0,5),xlim = c(0,1),main = "The original data graph")   # from the graph, need to fit as an exponential function
```
```{r pressure, echo=FALSE}
plot(x = u1,y = -5.000e-01*log(1-u1),ylim =c(0,5),xlim = c(0,1),main = "The graph of fitting function")
```
## Graphs in Q2
```{r pressure, echo=FALSE}
hist(y2,breaks = 8,main = "Histogram of Q2",xlab = "random numbers of Q2")
```
## Graphs in Q3
```{r pressure, echo=FALSE}
hist(num3_1,breaks = 8,main = "Histogram of Q3",xlab = "random numbers of Q3")
```
```{r pressure, echo=FALSE}
hist(num3_2,breaks = 8,main = "Histogram of Q3",xlab = "random numbers of Q3")
```
## Graphs in Q4
```{r pressure, echo=FALSE}
hist(num4,breaks = 8,main = "Histogram of Q4",xlab = "random numbers of Q4")
```

## Graphs in Q5
```{r pressure, echo=FALSE}
hist(y5,breaks = 8,main = "Histogram of Q5",xlab = "random numbers of Q5")
```
## Graphs in Q6
```{r pressure, echo=FALSE}
hist(c(un6,u6),breaks = 8,main = "Histogram of Q6",xlab = "random numbers of Q6")
```
